---
title: HRS
author: Andreas M. Brandmaier
date: 2023-05-02
repro:
  packages:
    - ggplot2
    - semtree
    - aaronpeikert/repro@adb5fa569
    - tidyverse
    - haven
    - here
  scripts:
    - R/preprocessing.R
    - R/tree.R
    - R/forest.R
  data:
    rndhrs: data/rndhrs_o.csv
output: html_document
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(repro)
# load packages from yaml header
automate_load_packages()
# include external scripts
automate_load_scripts()
```

## About

This project contains the code to (re)produce the SEM tree and forest analysis
reported in 

- Brandmaier, A. M., & Jacobucci, R. C. (2023). Machine learning approaches to structural equation modeling. In R. H. Hoyle (Ed.), _Handbook of structural equation modeling_ (2nd ed., pp. 722–739). Guilford Press.


## Reproducibility

This project is reproducible using the `repro` approach (see https://github.com/aaronpeikert/repro) as described by:

- Peikert, A., & Brandmaier, A. M. (2021). A reproducible data analysis workflow with R Markdown, Git, Make, and Docker. _Quantitative and Computational Methods in Behavioral Sciences_, 1, Article e3763. https://doi.org/10.5964/qcmb.3763

- Peikert, A., van Lissa, C. J., & Brandmaier, A. M. (2021). Reproducible research in R: A tutorial on how to do the same thing more than once. _Psych_, 3(4), 836–867. https://doi.org/10.3390/psych3040053

Note that for legal reasons, we cannot share the raw data, that is,
the analyses can only be reproduced if you obtain the HRS raw data
through official channels.

If you are unsure whether or not you have `git` `make` & `docker` on your system, try running this in your R console:

```{r, eval=FALSE}
check_git()
check_make()
check_docker()
```

## Preprocessing

The following code prepares the raw data for subsequent modeling.

```{r preprocessing}
if (!exists("data/rndhrs_subset.csv")) {
  source("R/preprocessing.R")
}
```

## SEM Tree Analysis

```{r tree}
# see R/tree.R
# this chunk (as long as it is empty, comments don't count) runs external
# code from scripts listed in the YAML
# see also https://yihui.org/knitr/demo/externalization/
```


## SEM Forest Analysis

```{r forest}
# see R/forest.R
# this chunk (as long as it is empty, comments don't count) runs external
# code from scripts listed in the YAML
# see also https://yihui.org/knitr/demo/externalization/
```
